---
title: "report"
author: "Nathan Faber and Thomas Jagielski"
date: 2020-11-27
output:
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(haven)
library(dplyr)
library(broom)
library(ggcorrplot)
library(corrplot)
library(modelr)

logit <- function(p) {
  odds_ratio <- p / (1 - p)
  log(odds_ratio)
}

inv.logit <- function(x) {
  exp(x) / (1 + exp(x))
}

convert_ever_lived_with_partner <- function(x) {
  case_when(
    x == 3 ~ 0,
    x == 2 ~ 2
  )
}
convert_met_online <- function(x) {
  case_when(
    x == 2 ~ 0,
    x == 3 ~ 1,
    x == 4 ~ 1,
    x == 5 ~ 1,
    x == 6 ~ 1,
    x == 7 ~ 1,
    x == 8 ~ 1,
    x == 9 ~ 1,
    x == 10 ~ 1
  )
}
convert_same_town <- function(x) {
  case_when(
    x == 3 ~ 0,
    x == 2 ~ 1
  )
}
```

## How Couples Meet and If They Stay Together

### Question
Are there predicting factors for if a couple are more likely to stay together or split up?  If so, can we model the likelihood of a couple staying together or splitting up based on inputs for the predicting factors?

### Dataset and Background
This project utilizes the HCMST (How Couples Meet and Stay Together) [https://data.stanford.edu/hcmst2017] This dataset was collected in 2017 and is made up of ~4,000 survey results from individuals 18+ that had been in a relationship previously. This survey is a remake of an earlier version of this survey with similar data. The data  contains a wide range of variables--all pertaining to the individual and their partner. Some examples of the data available include: Race, Religion, Level of Education, Sexual Orientation, How their relationship ended etc.

The survey  does have several notable quirks. The survey separates out an LGB group that was specifically sampled for. The survey was orchestrated through a rewards platform (KnowledgeBase) in which participants were compensated. This could introduce some form of sample bias. There were specific measures taken to attempt to get a representative sample, for example, random dialing of telephone numbers, as well as using address based sampling.

Given the above, this data source suits our purposes and will aid us in understanding which factors cause couples to stay together.

### EDA
As you have probably realized from above, this dataset is really quite large (3,500 rows by 285 columns)! 
One of the first things that we noticed was the enormous number of NA values in each column. Upon further investigation these NA’s are  intentional and indicate that the subject was not asked that question. Luckily we have access to the survey data (see the data folder of our repo) where we can see what each of the questions were and what constraints were needed for that question to be asked.

Put simply, there were more data and more question branches than we could deal with in our limited amount of time. We decided to focus on the questions on the married vs unmarried branches since that was in line with our end goal. Luckily, we found that for both the married and unmarried participants they were asked more or less the same question. For example, married couples would be asked if they met online, whereas couples that weren’t married would be asked an identical question. Due to the survey collection method the data was stored in different columns. To deal with this problem we used the tidyverse ```coalesce``` function to merge the two columns and get rid of NA values.

There were a myriad of other problems regarding the coding of the data. Some examples included:
- the dataset was almost entirely categorical variables
- data was in a STADA format which is proprietary
- naming conventions of columns required lots of manual lookups
- each question could also be “refused”
- factors had order but were not consistent across the dataset

### Loading and Processing Data
```{r load_data, include=FALSE}
df_raw <- read_dta(file = "./data/HCMST.dta")

df_column_rename <-
  df_raw %>%
    as.tibble() %>%
    rename(
      married = S1,
      current_partner_status = S2,
      ever_had_partner = S3,
      partner_sex = Q4,
      partner_same_sex = Q5,
      partner_latino_hispanic = Q6A,
      partner_race = Q6B,
      partner_age = Q9,
      partner_education_level = Q10,
      partner_mother_education_level = Q11,
      partner_polictial_belief = Q12,
      your_mother_education_level = Q14,
      #country_you_grew_up_in = Q15A1,
      #state_you_grew_up_in = Q15A2,
      #city_you_grew_up_in = Q15A3,
      #your_country_met_partner = Q15A4,
      #your_state_met_partner = Q15A5,
      #your_city_met_partner = Q15A6,
      met_partner_location = Q15A7,
      number_relatives_you_visit = Q16,
      times_married_inclusive = Q17A, # if S1=1
      times_married = Q17B, # if S1=2
      gender_sexually_attracted_to_1 = Q17C, # ppgender = 2
      gender_sexually_attracted_to_2 = Q17D, #ppgender = 1
      currently_living_with_partner = Q19,
      ever_lived_together_w_partner = Q20,
      date_met_year = Q21A_Year,
      date_met_month = Q21A_Month,
      date_relationship_began_year = Q21B_Year,
      date_relationship_began_month = Q21B_Month,
      date_first_lived_together_year = Q21C_Year,
      date_first_lived_together_month = Q21C_Month,
      date_married_year = Q21D_Year,
      date_married_month = Q21D_Month,
      sexual_orientation = w6_identity,
      outness = w6_outness,
      age_came_out = w6_outness_timing,
      income_disparity = Q23,
      #story_how_met = Q24,
      same_high_school = Q25,
      same_university = Q26,
      grow_up_same_town = Q27,
      parents_knew_each_other_before_met = Q28,
      mutual_friends_prior_1 = w6_friend_connect_1,
      mutual_friends_prior_2 = w6_friend_connect_2,
      mutual_friends_prior_3 = w6_friend_connect_3,
      mutual_friends_prior_4 = w6_friend_connect_4,
      met_online = Q32,
      relationship_quality = Q34,
      #realtionship_explaination = Q35,
      sex_frequency = w6_sex_frequency,
      other_date = w6_otherdate,
      number_others_dated = w6_how_many, # how many other people met with besides partner
      #how_met = w6_how_meet,
      dating_app_met_other = w6_otherdate_app,
      how_many_met_dating_app = w6_how_many_app,
      #most_commonly_used_dating_app = Q40,
      ever_married_to_partner = Past_Partner_Q1,
      relationship_end_nonmar = w6_relationship_end_nonmar,
      who_wanted_breakup_more_nonmar = w6_breakup_nonmar,
      marriage_end_mar = w6_relationship_end_mar,
      who_broke_up = w6_who_breakup,
      #reason_break_up = w6_why_broke_up,
      partner_same_sex_2 = Q5_2,
      partner_hispanic_latino_2 = Q6A_2,
      year_partner_born_2 = Q9B_2,
      partner_education_level_2 = Q10_2,
      partner_mother_education_level_2 = Q11_2,
      partner_polictial_belief_2 = Q12_2,
      your_mother_education_level_2 = Q14_2,
      #country_you_grew_up_in_2 = Q15A1_2,
      #state_you_grew_up_in_2 = Q15A2_2,
      #city_you_grew_up_in_2 = Q15A3_2,
      #your_country_met_partner_2 = Q15A4_2,
      #your_state_met_partner_2 = Q15A5_2,
      #your_city_met_partner_2 = Q15A6_2,
      met_partner_location_2 = Q15A7_2_1,
      number_relatives_you_visit_2 = Q16_2,
      times_married_2 = Q17B_2,
      gender_sexually_attracted_to_1_2 = Q17C_2, # ppgender = 2
      gender_sexually_attracted_to_2_2 = Q17D_2, #ppgender = 1
      ever_lived_together_w_partner_2 = Q20_2,
      date_met_year_2 = Q21A_2_Year,
      date_met_month_2 = Q21A_2_Month,
      date_relationship_began_year_2 = Q21B_2_Year,
      date_relationship_began_month_2 = Q21B_2_Month,
      date_first_lived_together_year_2 = Q21C_2_Year,
      date_first_lived_together_month_2 = Q21C_2_Month,
      date_married_year_2 = Q21D_2_Year,
      date_married_month_2 = Q21D_2_Month,
      date_broken_up_year_2 = Q21E_2_Year,
      date_broken_up_month_2 = Q21E_2_Month,
      date_partner_pass_year = Q21F_2_Year,
      date_partner_pass_month = Q21F_2_Month,
      sexual_orientation_2 = w6_identity_2,
      outness_2 = w6_outness_2,
      age_came_out_2 = w6_outness_timing_2,
      income_disparity_2 = Q23_2,
      #story_how_met_2 = Q24_2,
      same_high_school_2 = Q25_2,
      same_university_2 = Q26_2,
      grow_up_same_town_2 = Q27_2,
      parents_knew_each_other_before_met_2 = Q28_2,
      mutual_friends_prior_1_2 = w6_friend_connect_2_1,
      mutual_friends_prior_2_2 = w6_friend_connect_2_2,
      mutual_friends_prior_3_2 = w6_friend_connect_2_3,
      mutual_friends_prior_4_2 = w6_friend_connect_2_4,
      met_online_2 = Q32_2,
      other_date_2 = w6_otherdate_2,      
      number_others_dated_2 = w6_how_many_2, # how many other people met with besides partner
      dating_app_met_other_2 = w6_otherdate_app_2,
      how_many_met_dating_app_2 = w6_how_many_app_2      
      )
```
```{r convert_factor, include=FALSE}
df_data <-
  df_column_rename %>%
    mutate(across(everything(), as_factor))
```

```{r convert_type, include=FALSE}
df_filtered <- df_data 
df_filtered$married <- ifelse(is.na(df_filtered$married) | df_filtered$married == "Refused" ,
                              NA,
                              as.logical(!is.na(str_extract(df_filtered$married, "^Yes"))))


df_filtered$ever_had_partner <- ifelse(is.na(df_filtered$ever_had_partner) | df_filtered$ever_had_partner == "Refused" ,
                              NA,
                              as.logical(!is.na(str_extract(df_filtered$ever_had_partner, "^Yes"))))

df_filtered$partner_sex <- ifelse(is.na(df_filtered$partner_sex) | df_filtered$partner_sex == "Refused",
                                              NA,
                                              as.logical(!is.na(str_extract(df_filtered$partner_sex, "Male$"))))

df_filtered$same_high_school <- ifelse(is.na(df_filtered$same_high_school) | df_filtered$same_high_school== "Refused",
                                              NA,
                                              as.logical(!is.na(str_extract(df_filtered$same_high_school, "^Same"))))


df_filtered$same_university <- ifelse(is.na(df_filtered$same_university) | df_filtered$same_university== "Refused",
                                              NA,
                                              as.logical(!is.na(str_extract(df_filtered$same_university, "^Atten"))))

df_filtered$same_high_school_2 <- ifelse(is.na(df_filtered$same_high_school_2) | df_filtered$same_high_school_2== "Refused",
                                              NA,
                                              as.logical(!is.na(str_extract(df_filtered$same_high_school_2, "^Same"))))


df_filtered$same_university_2 <- ifelse(is.na(df_filtered$same_university_2) | df_filtered$same_university_2== "Refused",
                                              NA,
                                              as.logical(!is.na(str_extract(df_filtered$same_university_2, "^Atten"))))


df_filtered$parents_knew_each_other_before_met<- ifelse(is.na(df_filtered$parents_knew_each_other_before_met) | df_filtered$parents_knew_each_other_before_met == "Refused",
                                             NA,
                                             as.logical(!is.na(str_extract(df_filtered$parents_knew_each_other_before_met, "^Yes"))))

# df_filtered$grow_up_same_town <- ifelse(is.na(df_filtered$grow_up_same_town) | df_filtered$grow_up_same_town == "Refused",
#                                              NA,
#                                              as.logical(!is.na(str_extract(df_filtered$grow_up_same_town, "^Yes"))))

df_filtered$other_date <- ifelse(is.na(df_filtered$other_date) | df_filtered$other_date == "Refused",
                                             NA,
                                             as.logical(!is.na(str_extract(df_filtered$other_date, "^Yes"))))
df_filtered$other_date_2 <- ifelse(is.na(df_filtered$other_date_2) | df_filtered$other_date_2 == "Refused",
                                             NA,
                                             as.logical(!is.na(str_extract(df_filtered$other_date_2, "^Yes"))))


```

```{r create_new_columns_ended, include=FALSE}
df_filtered <- df_filtered %>%
  filter(married | ever_had_partner | !is.na(str_extract(current_partner_status, "^Yes"))   ) %>% 
  mutate(ever_married = coalesce(times_married_inclusive, times_married, times_married_2)) %>%
  mutate(has_married = if_else(ever_married== "Never married" , FALSE, TRUE))  %>%
  # Now look if marriage ended
  mutate(end = coalesce(relationship_end_nonmar,marriage_end_mar)) %>%
  mutate(ended = if_else(married == TRUE | !is.na(str_extract(current_partner_status, "^Yes")) | !is.na(str_extract(end, "deceased$")), FALSE, TRUE )) 

df_filtered %>% 
  select(married,has_married, current_partner_status, ended, relationship_quality)
```

```{r merge_columns}
# Lets merge the columns for people who got divorced and those who didn't
df_of_interest <- df_filtered %>% 
  mutate(gender_sexually_attracted_to = coalesce(gender_sexually_attracted_to_1, gender_sexually_attracted_to_2, gender_sexually_attracted_to_1_2, gender_sexually_attracted_to_2_2)) %>% 
  mutate(mutual_friends_prior_1 = coalesce(mutual_friends_prior_1, mutual_friends_prior_1_2)) %>%
  mutate(mutual_friends_prior_2 = coalesce(mutual_friends_prior_2, mutual_friends_prior_2_2)) %>%
  mutate(mutual_friends_prior_3 = coalesce(mutual_friends_prior_3, mutual_friends_prior_3_2)) %>%
  mutate(mutual_friends_prior_4 = coalesce(mutual_friends_prior_4, mutual_friends_prior_4_2)) %>%
  
  mutate(partner_education_level = coalesce(partner_education_level, partner_education_level_2)) %>%
  # mutate(times_married = coalesce(times_married_inclusive, times_married_2)) %>%
  mutate(ever_lived_together_w_partner = coalesce(ever_lived_together_w_partner, ever_lived_together_w_partner_2, currently_living_with_partner)) %>% 
  mutate(same_high_school = coalesce(same_high_school, same_high_school_2)) %>% 
  mutate(same_university = coalesce(same_university, same_university_2)) %>% 
  mutate(met_online = coalesce(met_online, met_online_2)) %>% 
  mutate(sexual_orientation = coalesce(sexual_orientation, sexual_orientation_2)) %>% 
  mutate(partner_polictial_belief = coalesce(partner_polictial_belief, partner_polictial_belief_2)) %>% 
  mutate(sexual_orientation = coalesce(sexual_orientation, sexual_orientation_2)) %>% 
  
  mutate(grow_up_same_town = coalesce(grow_up_same_town, grow_up_same_town_2)) %>%
  mutate(other_date = coalesce(other_date, other_date_2)) %>% 

  select(married, has_married, ended,
       ever_had_partner,
       relationship_end_nonmar,
       marriage_end_mar,
       ever_lived_together_w_partner,
       age_when_met,
       partnership_status,
       other_date,
       grow_up_same_town,
       partner_polictial_belief,
       sexual_orientation,
       met_online,
       same_high_school,
       same_university,
       who_broke_up,
       times_married,
       partner_education_level, 
       xlgb ,
       w6_same_sex_couple,
       gender_sexually_attracted_to,
       mutual_friends_prior_1,
       mutual_friends_prior_2,
       mutual_friends_prior_3,
       mutual_friends_prior_4,
       relationship_quality,
       partyid7,
       CaseID
  )

df_of_interest
```

### Correlation Matrix for Predictive Factors

In order to find if there were predictive factors for if someone was still in a relationship, we considered a correlation matrix for a variety of the factors.  By doing this, we could determine relationships between variables.  We considered the factors that had larger correlations with one being married, divorced, or separated.  Furthermore, by considering the correlation matrix we were able to simplify the model by considering one factor that was highly correlated with another.

```{r correlation_all_factors}
data <-
  df_of_interest %>%
    mutate(across(everything(), as_factor)) %>%
    # Default is 0 is false and 1 is true
    mutate(married = as.numeric(married) - 1,
           relationship_quality = as.numeric(relationship_quality),
           age_when_met = as.numeric(age_when_met),
           marriage_end_mar = as.numeric(marriage_end_mar),
           met_online = as.numeric(met_online),
           met_online = convert_met_online(met_online), # 0 = no; 1 = yes
           partner_polictial_belief = as.numeric(partner_polictial_belief),
           partyid7 = as.numeric(partyid7),
           political_diff = abs(partner_polictial_belief - partyid7),
           grow_up_same_town = as.numeric(grow_up_same_town), 
           grow_up_same_town = convert_same_town(grow_up_same_town), # 0 = no; 1 = yes 
           ever_had_partner = as.numeric(ever_had_partner),
           other_date = as.numeric(other_date) - 1, # 0 = no; 1 = yes
           same_high_school = as.numeric(same_high_school) - 1,
           same_university = as.numeric(same_university) - 1,
           sexual_orientation = as.numeric(sexual_orientation),
           ever_lived_together_w_partner = as.numeric(ever_lived_together_w_partner),
           ever_lived_together_w_partner = convert_ever_lived_with_partner(ever_lived_together_w_partner),
           xlgb = as.numeric(xlgb),
           ended = as.numeric(ended) - 1,
           partnership_status = as.numeric(partnership_status), # 1 = married; 2 = partnered_not_married; 3 = unpartnered, has had past partner
           who_broke_up = as.numeric(who_broke_up) - 1,  #1 = I wanted it more; 2 = partner wanted separation more; 3 = equal
           times_married = as.numeric(times_married) - 2,
           partner_education_level = as.numeric(partner_education_level) - 1, # 0 = LGB sample; 1 = gen pop
           w6_same_sex_couple = as.numeric(w6_same_sex_couple) - 1) # 0 = not same-sex couple; 1 = same-sex couple

complete_list <- 
  c("married", 
    "relationship_quality",
    "age_when_met",
    "marriage_end_mar",
    "met_online",
    "political_diff",
    "grow_up_same_town",
    "ever_had_partner",
    "other_date",
    "same_high_school",
    "same_university",
    "sexual_orientation",
    "ever_lived_together_w_partner",
    "xlgb",
    "ended",
    "partnership_status",
    "who_broke_up",
    "times_married",
    "w6_same_sex_couple")

complete_label <- 
  c("married" = "Married", 
    "relationship_quality" = "Relationship Quality",
    "age_when_met" = "Age When Met",
    "marriage_end_mar" = "Marriage Ended",
    "met_online" = "Met Online",
    "political_diff" = "Difference in Political Orientation",
    "grow_up_same_town" = "Grew up in the Same Town",
    "ever_had_partner" = "Ever had a Partner",
    "other_date" = "Dated Someone Else in Past Year",
    "same_high_school" = "Went to Same High School",
    "same_university" = "Went to Same University",
    "sexual_orientation" = "Sexual Orientation",
    "ever_lived_together_w_partner" = "Ever Lived With Partner",
    "xlgb" = "LGBTQ",
    "ended" = "Relationship/Marriage Ended",
    "partnership_status" = "Current Partnership Status",
    "who_broke_up" = "Who Broke Up",
    "times_married" = "Number of Times Married",
    "w6_same_sex_couple" = "Same Sex Couple")

data[ ,complete_list] %>%
  cor(use="pairwise.complete.obs", method = c("pearson", "kendall", "spearman")) %>%
  round(5) %>%
  ggcorrplot(show.diag = T, type = "full", lab = TRUE, lab_size = 2) +
  ggtitle("Complete Correlation Matrix for Broken Up Couples") + 
  scale_x_discrete(labels=complete_label) +
  scale_y_discrete(labels=complete_label)
```

**Observations**:
This correlation matrix is overpopulated with data, but allows us to observe general trends in correlation throughout the entire filtered dataset.  We can see that many factors have very little correlation between many of the factors.  Oftentimes the strong correlations are ones that express the same information or have a logical link.  For example, current partnership status has a strong negative correlation with married.  Since higher numbers of partnership status are divorced or separated and a higher number for marriage represents the individual being married, this correlation makes sense.  


In order to look at specific factors in more detail we will consider a reduced set below.

```{r correlation_selected_factors}
selected_list <- 
  c("married",
    "ended",
    "marriage_end_mar",
    "met_online",
    "ever_lived_together_w_partner",
    "w6_same_sex_couple",
    "age_when_met",
    "political_diff",
    "other_date")

data[ ,selected_list] %>%
  cor(use="pairwise.complete.obs", method = c("pearson", "kendall", "spearman")) %>%
  round(5) %>%
  ggcorrplot(show.diag = T, type = "full", lab = TRUE, lab_size = 2) +
  ggtitle("Correlation Matrix for Broken Up Couples Selected Factors") + 
  scale_x_discrete(labels=complete_label) +
  scale_y_discrete(labels=complete_label)
```

**Observations**:
From this correlation matrix we can see that having ever lived with a partner appears to have one of the strongest correlations with staying in a marriage.  We can also observe that same sex couples are less likely to married.  However, this could be influenced by political restrictions about same sex marriage in different regions of the United States.  Interestingly a large political difference has a positive correlation with the ending of a relationship or marriage; however, if we consider just the ending of a marriage it appears that there is a negative correlation between political difference and a marriage ended.  Similarly, there appears to be a negative correlation between political orientation and being married.  We can also observe that there is a positive correlation between someone having met their partner online and the age when they met.  Similarly, there appears to be a positive correlation between meeting someone online and being a same sex couple.


### Modeling

Using some of the factors that we found to have a strong correlation in the previous section, we were interested to see if we could create a model that would predict if someone would stay married or if their relationship would end.

```{r split_data}
n_train <- data %>%
  summarize(N = as.integer(n()/2)) %>%
  .$N

df_train <-
  data %>%
  slice_sample(n = n_train)
  

df_validate <-
  anti_join(
   data,
   df_train,
   by = "CaseID"
  )
```


Using the training set, we can create a model that predicts the ending of a relationship.

```{r create_model}
model_ended <-
  glm(
    formula = ended ~ met_online + ever_lived_together_w_partner + w6_same_sex_couple + age_when_met + political_diff,
    data = df_train,
    family = "binomial"
  ) 


model_ended %>%
  tidy(
    conf.int = TRUE,
    conf.level = 0.90
  )
```

**Observations**:
When considering the coefficients for our model we can see that there appears to be a negative correlation for meeting someone online and the relationship ending.  Similarly, there appears to be a negative correlation between ever having lived with partner and the relationship ending.  When considering the confidence intervals for these coefficients, it appears that the ranges do not include zero, which indicates significance in the model.  We can also observe that the confidence interval for ever having lived with your partner is smaller than for having met online.  The other factors we considered (same sex couple, age_when_met, and political difference) all appear to have positive correlation with the ending of a relationship.  None of the confidence intervals for these coefficients include 0, which indicates the significance for all of these factors within our model.  The age when a couple met appears to have the smallest confidence interval out of any of the factors considered within this model.


We will next validate our model on the validation dataset.

```{r validate_model}
df_validate_summary <-
  df_validate %>%
  add_predictions(model_ended, var = "log_odds_ratio") %>%
  arrange(log_odds_ratio) %>%
  rowid_to_column(var = "order") %>%
  mutate(pr_ended = inv.logit(log_odds_ratio)) %>%
  mutate(ended_prediction = ifelse(pr_ended >= 0.5, 1, 0)) %>%
  mutate(N = as.integer(n())) %>%
  filter(ended_prediction == ended) %>%
  mutate(N_correct = as.integer(n())) %>%
  summarize(percent_correct = N_correct / N) %>%
  summarize(mean(percent_correct))
  
df_validate_summary
```
**Observations**:
We find that using a log-odds threshold of 0.5% as the cutoff for an ending prediction (less than 0.5 indicates staying together; whereas, greater than 0.5 indicates splitting up), out model yielded the correct prediction for a separation approximately 85% of the time.  


Finally, we can input a test case into the model to predict the outcome of their relationship.

```{r apply_model}
data_test <- tibble(met_online = 0, 
                    ever_lived_together_w_partner = 1,  
                    w6_same_sex_couple = 0,  
                    age_when_met  = 26,
                    political_diff = 2,  
                    other_date = 0)

df_prediction <-
  data_test %>%
  add_predictions(model_ended, var = "log_odds_ratio") %>%
  arrange(log_odds_ratio) %>%
  rowid_to_column(var = "order") %>%
  mutate(pr_ended = inv.logit(log_odds_ratio)) %>%
  mutate(ended_prediction = ifelse(pr_ended >= 0.5, 1, 0)) # 0 = False; 1 = True

print.data.frame(df_prediction) # use to print the entire dataframe in knitted document 
#df_prediction
```
### Results
While this model is far from perfect it does indicate that certain factors can influence whether people are still together. We do not claim that this is the best model that could be created from this data. We were more interested in the process of creating this model than creating the best one. We could imagine taking into account more factors like age for better results. One cool thing about this model is that not only do we have confidence intervals for each of the coefficients calculated, we output a probability at the end. This allows us to see which factors are actually important. The final output of a probability is also cool because it allows us to compare two predictions side by side with some form of uncertainty. Likely the largest amount of uncertainty in this dataset is related to how well it fits the population. There were hints within the documentation of ways that the survey team tried to normalize this. Unfortunately, the documentation wasn't clear or detailed enough for us to use any of the work they had done 




### Remaining Questions / Where to next?

This was an eye opening project in several different ways. We ran into ethical questions of whether we should model relationships/human behavior as well as technical problems related to the whacky survey format. We have only scratched the surface of this dataset. There is tons more exploration that could be done. For example, the dataset has some normalization values to try and make their sample more representative of the population -- we didn’t factor this into any of our calculations. We also chose to look at a very small subset of the columns in a discretized way. One example of this is how we look at simply the end of marriages as separation or divorce, where the dataset differentiates. This means that there are likely many more trends present in this data that we didn’t look at.

Here are a few other things that we were interested in exploring:
- How are the predictors that influence whether relationships end changed with age?
- Can attributes about a relationship be accurately predicted based on other data (aka can we tell which couples met online?)
- In what cases does our prediction model break
- Are there significant differences in predictors for lgbt+ couples vs straight couples
- What are the implications of this work? Do dating apps employ something like this and is it alright/biased?





















